{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
4.1 new scenario / 4.2 transition

Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}
This class of words corresponds to \TB{highly specialized words? domain-specific? a hard limit on too complicated words?}

Finally the results for Clustering coefficient and Number of synonyms, despite some tendencies, do not allow us to conclude either to an effect or no effect of those features on substitution susceptibility.

@@

Next, we measure how a word $\wstart$'s feature varies as $\wstart$ is substituted by $\warrival$, i.e. $\phi(\warrival)$ as a function of $\phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$:
$$\nu_{\phi}(f) = \left<\phi(\warrival)\right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$

>>>>

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.  If these variables have an effect, it is by no means as strong as it is for Word frequency.  This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).  We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice higher than for the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).  Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest and late-learnt words are more susceptible.  To examine further this phenomenon, we plotted the two-dimensional map of joint susceptibility values for these two features (heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
\TB{We see that \todo{}}.
\TB{This class of words corresponds to \todo{} [\TB{highly specialized words? domain-specific? a hard limit on too complicated words?}]}
%Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
%These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}

All in all, apart for Word frequency and despite some tendencies these results do not allow us to conclude either to an effect or no effect of the selected psycholinguistic features on substitution susceptibility. We may therefore globally assume that substitution targets are more or less chosen in a uniform way with respect to these features.

% plus ou moins choisies uniformément (modulo les réserves exhibées en 4.1), on peut montrer en quoi elles sont modifiées Finally the results for Clustering coefficient and Number of synonyms, despite some tendencies, do not allow us to conclude either to an effect or no effect of those features on substitution susceptibility.

@@

Next, we can thus show how words are modified once we know they are substituted, \hbox{i.e.} how their features are modified by the said substitution.
We therefore measure how a word $\wstart$'s feature varies as $\wstart$ is substituted by $\warrival$, i.e. $\phi(\warrival)$ as a function of $\phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$:
$$\nu_{\phi}(f) = \left<\phi(\warrival)\right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$
